Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
deleted one letter
minor rephrasing and some comments

We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The SV of the strategy distraction contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
The estimated odds ratio indicated a higher chance of choosing distraction, when the SV of that strategy is higher.
Additionally, the SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
The estimated odds ration indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. 
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC.
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As one would expect, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).

>>>>

We then conducted an ordinal regression with the dependent variable "choice" and the individual SVs of all three strategies as independent variables.
Overall model fit was fair with $R^{2}=$ `r papaja::printnum(Choice_OrdReg_R2)`.
The SV of the strategy distraction contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$distraction_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[2,2])`).
The estimated odds ratio indicated a higher chance of choosing distraction, when the SV of that strategy is higher.
Additionally, the SV of the strategy suppression contributed significantly to the model (`r papaja::apa_print(Choice_OrdReg)$full_result$suppression_sv`, $BF10=$ `r papaja::printnum(Choice_OrdReg_Posterior$BFtu_exploratory[4,3])`).
The estimated odds ratio indicated that a participant is more likely to later choose suppression, when the SV of the strategy suppression is higher.

@@

We exploratorily wanted to investigate the influence of self-control and the investment trait Need for Cognition (NFC) on individual SVs of ER strategies.
The starting point for this was the model reported before. <!-- welches model genau? -->
Only predictors that had previously shown a significant association with SVs were included in the model together with level-2 predictors self-control and NFC. <!-- ist das wirklich zulässig? Ich hab mich gefragt, ob das nich zu Kritik von den Reviewern führen könnte, dass ihr hier nur die vorher sign. predictors auswählt.-->
The third model followed the specification:
$$
\begin{split}
SV \sim \text{effort rating} + \text{utility rating} + corrugator \text{ activity} \\\ \text{self-control} + \text{NFC} + (1 |subject)
\end{split}
$$
As expected, the predictors effort rating (`r papaja::apa_print(MLM_3)$full_result$effort_cwc`) showed a negative association with SVs, while utility rating (`r papaja::apa_print(MLM_3)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_3)$full_result$Corr_cwc`) showed a significant positive association with SVs.
In addition, a positive association was also found between self-control and SVs (`r papaja::apa_print(MLM_3)$full_result$SC_gmc`).
However, the effect size of self-control was negligibly small ($f^{2}=$ `r papaja::printnum(Exp_M3_table[5,5], digits = 3)`).
Detailed information can be found in the [supplementary material](#SupplementExploratory).
